% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %

\documentclass[a4paper,10pt]{article}

\newcommand{\hwNumber}{2}

\input{../algtop_preamble.tex}
\input{../.modules/basics/biblatex.tex}

%%% ID: sensitive, do NOT publish!
%\InputIfFileExists{../id.tex}{}{}

\begin{document}
\maketitle
\pagestyle{headings}
\pagenumbering{arabic}
\thispagestyle{empty}

	\begin{enumerate}
	\item \textbf{Morphism between coverings is covering:}
	
	For $F_i \to E_i \xrightarrow{p_i} B$: coverings in $\mop{Cov}_0(B)$ with $E_i$: connected and $B$: path connected and locally path connected, the following diagram commutes:
	\begin{center}
	\begin{tikzcd}[row sep=5ex,column sep=3em]
		E_1
			\arrow{rr}{f}
			\arrow[swap]{dr}{p_1} & &
		E_2
			\arrow{dl}{p_2} \\
		& B &
	\end{tikzcd}
	\quad
	$\begin{gathered}
%		p_1 = p_2 \circ f,\\
		e_2 = f(e_1),\\
		b = p_1(e_1) = p_2(e_2),
	\end{gathered}$
	\end{center}
	To show that $f$ is itself a covering, we need only verify that $f$ is locally trivial with some discrete fiber $F$. 
	In fact, given any $e_2\in E_2$ and $b = p_2(e_2)$, there exists some neighborhood $U\subset B$ that the following diagram holds (by restriction):
	\begin{center}
	\begin{tikzcd}[row sep=5ex,column sep=2.5em]
		U\times F_1
			\arrow{rr}{f}
			\arrow[swap]{dr}{p_1} & &
		U\times F_2
			\arrow{dl}{p_2} \\
		& U &
	\end{tikzcd}
	\quad
	$\begin{aligned}
		e_1 &= \pqty\big{b,k_1},\\
		e_2 &= \pqty\big{b,k_2(b,k_1)},
	\end{aligned}
	\quad k_i \in F_i
	$
	\end{center}
	
	Generally, $k_2 = k_2(b,k_1)$ depends on the base point $b \in B$. However, since $B$ is locally path connected, we can restrict $U$ to be path connected, while $k_2\in F_2$: discrete. Since continuous maps preserve path connectedness, $k_2$ is in fact independence of $b$, i.e.\ $k_2 = \varphi(k_1)$. 
	
	On the other hand, $\forall\ e_2 = (b,k_2)\in U\times\{k_2\}\subset E_2$, we have its preimage $f^{-1}(e_2) = \{b\}\times\varphi^{-1}(k_2)$. Note that $E_2$ is connected while $\varphi^{-1}(k_2) \in F_1$ is discrete; for the same reasoning as above, $\varphi^{-1}(k_2) = F$ is in fact independent of $k_2$. This is the discrete fiber $F$ we have been looking for. Hence $f$ is also a covering map\footnote{
		Reference: \https{math.stackexchange.com/a/109774}. 
	}. \qedfull
	
	\item \textbf{Cylinder with ends pinched --- $\pi_1$ and universal cover:}
	\begin{equation}
		Y = \flatfrac{(X\times I)}{(X\times \pd I)},
		\quad I = [0,1]
	\end{equation}
	Note that $Y$ is homeomorphic to two cones\footnote{
		See discussions from Problem Set \textnumero 1. 
	} $CX_1\coprod CX_2$ with ``bases'' $X_i\subset CX_i$ and ``vertices'' $v_i$~respectively identified: $X_1\sim X_2,\ v_1\sim v_2\equiv v$. $X$ is path connected and so is $Y$, hence we are free to choose $\pi_1(Y) = \pi_1(Y,y_0)$. 
	
	First note that paths that do \textit{not} pass through the vertex $v$ are all homotopic, since they are contained in a cone and cones are contractible\footnote{
		$[\gamma_1]
		= [\gamma_2\star\gamma_2^{-1}\star\gamma_1]
		= [\gamma_2]$. 
	}. Therefore all contributions to $\pi_1(Y)$ are loop classes that \textit{do} pass through the vertex $v$. 
	In other words, morphisms in $\Pi_1 Y$ are in one-to-one correspondence with morphisms in:
	\begin{equation}
		\Pi_1\pqty\big{[0,1]/_{0\sim 1}} = \Pi_1 S^1
	\end{equation}
	Therefore, $\pi_1(Y) \cong \pi_1(S^1) = \mbb{Z}$. 
	\qed
	
	The universal cover $\tilde{Y}$ of $Y$ can be constructed by assigning an induced topology to the space of path classes, same as in the general proof of its existence. Since $Y$ is ``degenerate'' at its vertex, this is equivalent to ``cutting open'' $Y$ at its vertex $v$, and joining $\mbb{Z}$ copies them end-to-end. More explicitly, it can be written as:
	\begin{equation}
		\tilde{Y} = {(X\times \mbb{R})}\Big/{
			\sim
		}\,,\quad
		(x,n)\sim (x',n),\ \forall\ 
			x\in X,\,n\in\mbb{Z}
	\end{equation}
	While the covering map: $\tilde{Y}\ni[x,t]\mapsto [x,t-\lfloor t\rfloor]\in Y$, here $\lfloor t\rfloor$ is the integer part of $t\in\mbb{R}$. 
	\qedfull
	
	\item \textbf{$\pi_1$ of fiber in fibration:}
	\label{item:fibration_fundamental}
	\begin{center}
	\begin{tikzcd}[row sep=8.5ex,column sep=7ex]
		X\times\{0\}
			\arrow[r]
			\arrow[hook,d] &
		E
			\arrow[d,"p"] \\
		X\times I
			\arrow[r,"f"]
			\arrow[ur,dashed,"\exists\,\tilde{f}"] &
		B
	\end{tikzcd}
	\end{center}
	
	For $F \to E \xrightarrow{p} B$: fibration, by homotopy lifting property (HLP), any homotopy in $B$ can be uniquely lifted to path class in $E$, provided some \textit{``initial condition''} $X\times\{0\}$. 
	This leads to the following results:
	
	\begin{enumerate}
	\item For $B$: simply-connected, take any loop class $[\tilde{\gamma}]\in\pi_1(E,e)$ as initial condition; its projection $[p\circ\tilde{\gamma}]\in\pi_1(B,b) = \Bqty\big{[\idty_b]}$ is trivial, i.e.\ $p\circ\tilde{\gamma} \simeq \idty_b$. By HLP, such homotopy can be lifted into $E$, i.e.
	\begin{equation}
		p\circ\tilde{\gamma} \simeq \idty_b
		\quad\xRightarrow{\ \text{lift}\,\ }\quad
		\tilde{\gamma} \simeq \tilde{\gamma}',\quad
		p\circ\tilde{\gamma}' = \idty_b
	\end{equation}
	In other words, $
		\tilde{\gamma}
		\simeq \tilde{\gamma}' \subset p^{-1}(b)
	$, i.e.\ any loop in $E$ is homotopic to some loop in $p^{-1}(b) \cong F$. This implies a surjective group homomorphism $
		\pi_1(p^{-1}(b),e)\to \pi_1(E,e)
	$, i.e.\ an epimorphism. 
	\qed
	
	\item For $E$: simply-connected, take any loop class $[\gamma]\in\pi_1(B,b)$ and consider its lifting $[\tilde{\gamma}]$. Note that in general $\tilde{\gamma}$ is \textit{not} a loop; however, we have $p\circ\tilde{\gamma} = \gamma$, hence $\tilde{\gamma}(0),\tilde{\gamma}(1)\in p^{-1}(b)$. In general, we have:
	\begin{equation}
		\gamma \simeq \gamma'
		\quad\xRightarrow{\ \text{lift}\,\ }\quad
		\tilde{\gamma} \simeq \tilde{\gamma}',\quad
		p\circ\tilde{\gamma}^{(\prime)}
		= \gamma^{(\prime)}
	\end{equation}
	By continuity, $\tilde{\gamma}(0),\tilde{\gamma}'(0)\in F_0$: a path component of $p^{-1}(b)$; similarly, $\tilde{\gamma}(1),\tilde{\gamma}'(1)\in F_1$. In other words, the start and end points of $\tilde{\gamma}$ are confined in path components $F_0$ and $F_1$, respectively. Hence a loop class in $\pi_1(B,b)$ maps to \textit{transport} between path components:
	\begin{equation}
	\begin{aligned}
		T_{(\cdot)}(e) \colon\ %
		\pi_1(B,b)
		&&&\longto &&
		\pi_0\pqty\big{p^{-1}(b)}\\[.5ex]
		[\gamma]
		&&&\longmapsto &&
		T_{[\gamma]}(e)
%		\colon\ %
%		\pi_0\pqty\big{p^{-1}(b)}
%		\longto \pi_0\pqty\big{p^{-1}(b)}
	\end{aligned}
	\end{equation}
	
	As a matter of fact, $T_{(\cdot)}(e)$ is a bijection. For $
		T_{[\gamma]} = T_{[\gamma']}
	$, they are characterized by two lifted paths $\tilde{\gamma},\tilde{\gamma}'$; since $E$ is simply connected, they are always homotopic: $
		\tilde{\gamma}\simeq\tilde{\gamma}'
	$, hence $
		[\gamma] = [\gamma']
	$ by projection $p$. This means that $T$ is injective. Surjectivity also follows from projection $\gamma = p\circ\gamma'$. Therefore, $T_{(\cdot)}(e)$ gives a bijection between $
		\pi_1(B,b)
	$ and $
		\pi_0\pqty\big{p^{-1}(b)}
	$. \qedfull
	
	\end{enumerate}
	
	\item \textbf{Pull-back of fibration is fibration:}
	\begin{center}
	\begin{tikzcd}[row sep=9ex,column sep=8ex]
		Y\times\{0\}
			\arrow[r]
			\arrow[d,hook] &[-1.2em]
		f^*(E)
			\arrow[r]
			\arrow[d] &
		E
			\arrow[d,"p"] \\
		Y\times I
			\arrow[r,"G"]
			\arrow[urr%
				,"\ \exists\,\tilde{F}\ %
					\text{(HLP)}"
				,swap
				,crossing over
			]
			\arrow[ur,dashed%
				,"\exists\,\tilde{G}"
			] &
		X
			\arrow[r,"f"] &
		B
	\end{tikzcd}\\[2ex]
	$
		(x,e) \in f^*(E)\subset X\times E,\quad
		f(x) = p(e)
	$
	\end{center}
	
	We need only verify that $f^*(E)\to X$ also has HLP, i.e.\ the existence of $\tilde{F}$ in the above diagram\footnote{
		Notice that $f^*(E)$ is the limit of the diagram, hence this is automatically true by the universal property of $f^*(E)$. I would like to thank \textit{刘逸华} for pointing this out. For now, we will stick to a more traditional proof. 
	}. By HLP of $
		E\xrightarrow{p} B,\ %
		\exists\ \tilde{F}\colon Y\times I \to E
	$ as shown above. We can use $\tilde{F}$ to construct $\tilde{G}$ explicitly; in fact, first consider:
	\begin{equation}
	\begin{aligned}
		\tilde{G} \colon\ %
		Y\times I
		&&&\longto &&
		X\times E\\
		(y,t)
		&&&\longmapsto &&
		\pqty\big{G(y,t),\tilde{F}(y,t)}
%		\colon\ %
%		\pi_0\pqty\big{p^{-1}(b)}
%		\longto \pi_0\pqty\big{p^{-1}(b)}
	\end{aligned}
	\end{equation}
	Note that $
		f\circ G = p\circ \tilde{F}
	$; compared with the definition of $f^*(E)$, this implies that the image of $\tilde{G}$ lies within $
		f^*(E)\subset X\times E
	$, hence after restriction of its codomain, $\tilde{G}$ becomes a well-defined lifting of $G$ into $f^*(E)$. Therefore, $f^*(E)\to X$ has HLP, i.e.\ it is also a fibration. \qedfull
	
	\item \textbf{More properties of fibration:}
	
	\begin{enumerate}
	
	\item By HLP, given any initial condition $e\in p^{-1}(b_1)$, lifting of any path $b_1\xrightarrow{\gamma} b_2$ exists. The lifted path with dependence of $e$ can then be written as $F\colon p^{-1}(b_1)\times I\to E$. 
	This is just a generalization of \ref{item:fibration_fundamental} for non-loop paths. 
	\qed
	
	\item Similarly, transport $T_{[\gamma]}$ defined in \ref{item:fibration_fundamental} can be generalized for non-loop paths. $T_{[\gamma]}$ is well-defined for path class $[\gamma]$, since by HLP homotopic paths can be lifted to homotopy in $E$. Therefore, the transport is fixed up to homotopy, i.e.
	\begin{equation}
	\begin{aligned}
		T \colon\ %
		\Hom_{\,\Pi_1 B} (b_0,b_1)
		&&&\longto &&
		\Hom_{\,\Cat{hTop}} \pqty\big{
			p^{-1}(b_0),p^{-1}(b_1)
		}
		\\[.5ex]
		[\gamma]
		&&&\longmapsto &&
		T_{[\gamma]}
	\end{aligned}
	\end{equation}
	Note that $T$ defined in this way is also independent of the choice of $F$, since $F$ simply specifies the starting point of the lifted path; no matter which $F$ we choose, the lifted paths will always be homotopic in $E$. Hence $T$ is well-defined in the above sense.
	\qed
	
	\item $T$ defined above is a functor: $
		\Pi_1 B\to \Cat{hTop}
	$. To verify this, we need only check that it is compatible with composition and maps identity morphisms to identity morphisms. Indeed, $
		T_{[\idty_b]} = [\idty_{p^{-1}(b)}]
	$, and $
		T_{[\gamma']\star[\gamma]}
		= T_{[\gamma'\star\gamma]}
		= T_{[\gamma']} \circ T_{[\gamma]}
	$ by joining two lifted paths (up to homotopy).
	\qed
	
	\item For $B$: path connected, there exists an isomorphism between any two objects in $\Pi_1 B$ (a path connecting any two points in $B$), which is mapped to isomorphisms between fibers $p^{-1}(b)$ in $\Cat{hTop}$. Hence any two fibers of $E\xrightarrow{p} B$ have the same homotopy type. 
	\qedfull
	
	\end{enumerate}
	\end{enumerate}

\printbibliography[%
%	title = {参考文献} %
	,heading = bibintoc
]
\end{document}
